RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2023-10-22 arxiv.tex
:triangular_flag_on_post: JSAC 231022

		\begin{remark}
			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Long2020a,Liang2020,Guo2019b,Qian2019b,Ding2020,Hassani2023,Zhou2019a,Wu2021a,Xu2021a,Yang2021a,Yang2018,Han2021,Zhang2022,Dai2023}.
			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
			\label{re:non_gaussian}
		\end{remark}

>>>>

		\begin{remark}
			We have assumed Gaussian codebook for the primary source and finite support for the backscatter nodes, since they are relatively practical and widely adopted in relevant literatures \cite{Qian2019b,Xu2020b,Zhang2021d,Hua2022,Hu2021a,Qian2019}.
			The proposed framework is extendable to non-Gaussian primary source, and the conditional \gls{pdf} \eqref{eq:energy_distribution} can be approximated using \gls{clt} for large $N$.
			\label{re:non_gaussian}
		\end{remark}
